---
title: "Evolution & regulation of rice inflorescence development"
author: "Tom Harrop<br>thomas.harrop@ird.fr<br>"
date: "24 May 2016"
output:
  ioslides_presentation:
    self_contained: false
    smaller: true
    transition: "faster"
    widescreen: true
    css: css/overrides.css
    fig_width: 9.16
    fig_height: 4.5
    keep_md: true
    logo: img/logo.svg
---

```{r setup, include=FALSE, results="hide"}

library(ggplot2)

# for proper scaling in the html, the figures should be:
# w    x    h
# 879       432  px
# 9.16      4.5  in
# for slides with subtitles:
# w    x    h
# 879       432  px
# 9.16      4  in

theme_slide <- theme_grey(base_size = 16, base_family = "Lato") +
  theme(
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA))
knitr::opts_chunk$set(
  dev.args=list(bg = "transparent", family = "Lato"),
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  dpi = 300)
source("src/plots.R")
```

## Rice facts

*  IRD people know this stuff

## Rice inflorescence architecture

```{r panicle}
my.img <- png::readPNG("img/panicle.png")
grid::grid.raster(my.img)
```

## Branching complexity is related to yield

```{r ptypes2}
print(ptypes2)
```

## Meristem identities

```{r pandev}
my.img <- png::readPNG("img/pan_dev.png")
grid::grid.raster(my.img)
```

## Meristem transitions & branching | *TAWAWA1* / *G1 LIKE PROTEIN 5*

Content

<footer class="source2">Yoshida <em>et al</em>., 2013. <a href="http://www.pnas.org/content/110/2/767.full">10.1073/pnas.1216151110</a></footer>

## Meristem transitions & branching | *LONELY GUY 1*

Content

<footer class="source2">Kurakawa <em>et al</em>., 2007 <a href="http://www.nature.com/nature/journal/v445/n7128/full/nature05504.html">10.1038/nature05504</a></footer>

## Laser microdissection (LMD) {.centered .flexbox .vcenter}

```{r lmd2}
my.img <- png::readPNG("img/lmdFigure.png")
grid::grid.raster(my.img)
```

## LMD experiments:

*   clusters -> ALOG genes
*   tf families -> HD-ZIP IV

## Applications of LMD data

*   functional characterisation
*   gene regulatory network
*   correlation with phenotypic diversity

## Diversity in panicle architecture

Content

## Domestication of Asian rice

```{r as}
print(as.genes)
```

## Domestication of African rice

```{r af, fig.width=9.16/2}
print(af.genes)
print(af.genes2)
```

## Parallel evolution

```{r dom}
print(dom.genes)
```

## Last slide

*  blah
*  blah